Relationships between environmental variabels and species richness

### 2015-02-08 Doc/ms.Rmd
methods of ms
results and references of ms

>>>>

# Methods

Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use

\begin{equation}
\text{var}(X) = p(1-p)
\end{equation}

## Results

Insert tables:

```{r table,results='asis',echo=FALSE}
load("../R/.RData")
library(knitr)
kable(sprich)
```

Or put results inline, e.g. the mean species richness is `r meansprich`.

<!-- 
Or you can type tables by hand:

Col A             Col B       Col C                   Col D
------------      -------     ------------------      ------------------
row 1             190         $112 \pm 2$             $233 \pm 3$
$\eta$            0.13        0.12                    0.12
$\eta^2$          0.14        0.13                    0.50
$\eta^3$          0.15        0.31                    0.52

Using `xtable` package in R:

```{r echo=F,results='asis',warning=F,message=F}
library(xtable)
data(tli)
## Demonstrate aov
 ## Taken from help(aov) in R 1.1.1
 ## From Venables and Ripley (1997) p.210.
 N <- c(0,1,0,1,1,1,0,0,0,1,1,0,1,1,0,0,1,0,1,0,1,1,0,0)
 P <- c(1,1,0,0,0,1,0,1,1,1,0,0,0,1,0,1,1,0,0,1,0,1,1,0)
 K <- c(1,0,0,1,0,1,1,0,0,1,0,1,0,1,1,0,0,0,1,1,1,0,1,0)
 yield <- c(49.5,62.8,46.8,57.0,59.8,58.5,55.5,56.0,62.8,55.8,69.5,55.0,
+            62.0,48.8,45.5,44.2,52.0,51.5,49.8,48.8,57.2,59.0,53.2,56.0)
 npk <- data.frame(block=gl(6,4), N=factor(N), P=factor(P), K=factor(K), yield=yield)
 npk.aov <- aov(yield ~ block + N*P*K, npk)
 op <- options(contrasts=c("contr.helmert", "contr.treatment"))
 npk.aovE <- aov(yield ~  N*P*K + Error(block), npk)
 options(op)

 xsum <- xtable(summary(npk.aov))
print(xsum,
      floating=F,
      hline.after=NULL,
      add.to.row=list(pos=list(-1,0, nrow(xsum)),
      command=c(
           '\\toprule\n',
          '\\midrule\n',
           '\\bottomrule\n')))
```
 -->

How about figures? We illustrate this in Fig. \ref{f:plot}.

[f:plot]: Figs/plot.pdf
![Caption here.\label{f:plot}][f:plot]

# References
